---
title: "Corona virus analysis"
author: "Ante Cobanov"
date: "3/31/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
```

### Start

Clear variables and close windows 

```{r a1, echo=TRUE}
graphics.off()
rm(list = ls(all=TRUE))
```

### Loading packages

```{r a2, echo=TRUE,results='hide', message=FALSE, warning=FALSE}
# packages
packages = c("tidyverse","coronavirus","purrr","eurostat","httr",
             "jsonlite","kableExtra","curl","jsonlite")
# install missing packages
lapply(packages, function(x) if (!(x %in% installed.packages())) {install.packages(x)})
#add packages
lapply(packages, library, quietly = TRUE, character.only = TRUE)
```

### Getting the data from GitHub 
#### variable <data> is a named list (name: country name, list element: data.frame)
#### date.frame columns are: date, confirmed, deaths, recovered

```{r}
data <- fromJSON("https://pomber.github.io/covid19/timeseries.json")
# glimpse(data)
tail(data[['Croatia']])
```

##### Create vector of EU countries names and vector of Croatian neigbours countries names 

```{r}
eu_countries <- c("Austria","Belgium","Bulgaria","Croatia","Cyprus","Czechia","Denmark","Estonia","Finland",
                  "France","Germany","Greece","Hungary","Ireland","Italy","Latvia","Lithuania","Luxembourg",
                  "Malta","Netherlands","Poland","Portugal","Romania","Slovakia","Slovenia","Spain","Sweden")

croatia_neighbours <-c("Italy","Slovenia","Serbia","Bosnia and Herzegovina","Hungary","Montenegro","Croatia")

countries <- names(data)
```

##### create named list (dfs_eu) of EU countries data frames 

```{r}
dfs_eu <- purrr::map(eu_countries,function(x) data[[x]] %>%  mutate(country=x))
names(dfs_eu) <- eu_countries
tail(dfs_eu[["Italy"]])
```

##### create long data frame (df_eu_long) from list of data frames

```{r}
df_eu_long <- bind_rows(dfs_eu)
countries1 <- df_eu_long %>% 
  select(country) %>% 
  distinct() %>%
  pull(country)
countries1[1:10]
```

##### create wide data frame for CONFIRMED cases

```{r}
# confirmed data frame
df_eu_wide_conf <- df_eu_long %>% 
  select(date,country,confirmed) %>% 
  pivot_wider(names_from=country,values_from=confirmed)
tail(df_eu_wide_conf)
```

##### create wide data frame for DEATHS

```{r}
# deaths data frame
df_eu_wide_deaths <- df_eu_long %>% 
  select(date,country,deaths) %>% 
  pivot_wider(names_from=country,values_from=deaths)
tail(df_eu_wide_deaths)
```

##### create wide data frame for RECOVERED cases

```{r}
# recovered data frame
df_eu_wide_recov <- df_eu_long %>% 
  select(date,country,recovered) %>% 
  pivot_wider(names_from=country,values_from=recovered)
tail(df_eu_wide_recov)
```

##### calculate wide data frame for NEW cases

```{r}
# calculation of new cases
df_eu_wide_new <- df_eu_wide_conf %>% 
  select(-c(date)) %>% 
  map(.,function(x) x-dplyr::lag(x)) %>% 
  bind_cols()
tail(df_eu_wide_new)
```


```{r}

df <- df_eu_long %>% 
  filter(country %in% c('Croatia','Slovenia'))



```


